---
title: "Clean Tampa County Files First"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Step 0: Read in libraries 
```{r, message=FALSE, warning=FALSE}
rm(list=ls())
library(tidyverse)
library(purrr)
library(data.table)
```


Step 1: Set working directories
```{r}
my_directory <- "/Users/fanny/Google Drive/db/usTransportation/data"
setwd(my_directory)
```

Step 2: Capture a list of files in directory
```{r}
files <- list.files(my_directory, pattern="*.csv", full.names=TRUE) 
#files
```


Step 3: Read in files and combine
```{r}
read_county_files <- function(filename){
    x <- fread(filename, skip=0, na.strings = c("(X)"))
    
    # obtain the path, which has the year in filename
    x <- mutate(x, Filename=sub(my_directory, "", filename))
    return(x)
}

combined <- map_df(files, read_county_files)
#View(combined)
```


Step 4: Create function for reading in filename string
split on the underscore (_)  
For example:
create array from filename "ACS_16_1YR_S0801"
which looks like c("ACS", "16", "1YR", "S0801")
we can pull out the year 16 from the array  
```{r}
strsplit_that_works <- function(cell, entity_requested) {
  x <- strsplit(cell, "_")
  y <- x[[1]][entity_requested]
  return(y)
}
```




Step 5: Only keep columns that start with HC01  
Since we're not interested in male and female marginal counts, let's only keep the total counts.   
```{r}
processed_frame <- combined %>%
  mutate(year = map_chr(Filename, strsplit_that_works, 2)) %>% 
  select(-starts_with("HC02")) %>% 
  select(-starts_with("HC03"))
View(processed_frame)
```

Step 6: Sanity check  

show that the year variable exists for the data frame  
```{r}
#select(processed_frame, year)
```

Sanity check: select the variable of interest HC01_EST_VC52  
```{r}
#select(processed_frame, starts_with("HC01_EST_VC52"))
```



Step 7: Write out
```{r}
write_csv(processed_frame, "processed_american_factfinder_transportation.csv")
```










